A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-09 docs/methods/erosion_methods.tex
NM

In closely related work, Mitchell \& Spagnolie developed methods to simulate viscous erosion in three dimensions  \cite{mit-spa2016}. That work employed a traction integral equation to solve for the surrounding Stokes flow. The advantage to this formulation is that it immediately provides the shear stress required to evolve boundaries. However, the standard double-layer potential used here will allow us to compute certain quantities in the fluid bulk, such as vorticity and pressure, that will facilitate our understanding of the erosion process. Furthermore, our primary aim is to simulate the erosion of multiple bodies held fixed within a porous network, whereas Mitchell \& Spagnolie simulated a single eroding body that is mobile.

>>>>

In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}. Their formulation was flexible enough to simulate a {\em mobile} body that erodes in various background flows (uniform flow, shear flow, etc.). An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.

Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations. Thus, instead of a single, mobile body, we will consider multiple, immobile bodies.
Rather than the traction-formulation, we will employ a standard double-layer formulation which will easily allow us to compute bulk quantities such as pressure and vorticity as a post-processing step.

%That work employed a traction integral equation to solve for the surrounding Stokes flow. The advantage to this formulation is that it immediately provides the shear stress required to evolve boundaries. However, the standard double-layer potential used here will allow us to compute certain quantities in the fluid bulk, such as vorticity and pressure, that will facilitate our understanding of the erosion process. Furthermore, our primary aim is to simulate the erosion of multiple bodies held fixed within a porous network, whereas Mitchell \& Spagnolie simulated a single eroding body that is mobile.
